linguistic_analysis_C-D.Rmd : Linguistic quantity and complexity

### 2021-06-08 code/linguistic_analysis_C-D.Rmd
blockNum and ttr

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
```

@@

d_flowers<- read_csv(here(data_location, "raw_chat.csv"))%>%
 filter(!is.na(text))
```

### 1. Utt Length
```{r utt_length}
#1.

d_flowers <- d_flowers %>%
  mutate(utt_length_words = str_count(text, "\\W+") + 1) %>% 
    group_by(gameId, blockNum, trialNum, repNum, playerId)

d_flowers_utt_length <- d_flowers %>%
      summarise(total_num_words = sum(utt_length_words))

ggplot(d_flowers_utt_length, aes(x=trialNum, y=total_num_words, color=as.factor(playerId)))+
  scale_color_brewer(palette="Dark2")+
  facet_wrap(~gameId, nrow=1) +
  geom_jitter(alpha=.05)+
  geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  stat_summary(fun.data = "mean_cl_boot")+
  scale_y_continuous(limits = c(0,50))+
  labs(title="Number of words", y="Number of words", x="Round number", color="playerId")+
  theme(legend.position="bottom")
```

### 2a. Number of turns
```{r number_of_turns}

d_flowers_n_turns <- d_flowers %>%
  summarise(n=n())

ggplot(d_flowers_n_turns, aes(x=trialNum, y=n, color=as.factor(playerId)))+
  facet_wrap(~gameId, nrow=1) +
  scale_color_brewer(palette="Dark2")+
  geom_jitter(alpha=.05)+
  geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  stat_summary(fun.data = "mean_cl_boot")+
  labs(title="Number of turns", y="Number of turns", x="Round number", color="playerId")+
  theme(legend.position="bottom")

```
### 2b. Number of turns
```{r number_of_turns2}

@@

ggplot(d_flowers_n_utt_speaker, 
       aes(x=trialNum, y=n_utt_speaker, label=playerId)) + 
  geom_smooth(method = "lm", formula = y~x) + 
  geom_point(alpha=.1) +
  facet_wrap(~ playerId) +
  xlab("Round number") + 
  ylab("Number of turns") + 
  theme_bw()
```

@@

@@

#ggplot(d_flowers_n_utt_dist, 
#       aes(x=trialNum, y=overall_turns, label=playerId)) + 
#  geom_smooth(method = "lm", formula = y~x) + 
#  geom_point(alpha=.1) +
#  facet_wrap(~playerId)+
#  xlab("Round number") + 
#  ylab("Proportion of turns") + 
#  theme_bw()

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
library(tidyverse)
library(here)
library("stringr")
```

@@

d_flowers<- read_csv(here(data_location, "raw_chat.csv"))%>%
 filter(!is.na(text))

### 1. Utt Length
```{r utt_length}

d_flowers_utt_length <- d_flowers %>%
  mutate(text = gsub('[[:punct:] ]+',' ',text)) %>%
  mutate(utt_length_words = sapply(strsplit(text, " "), length)) %>% 
  group_by(gameId, blockNum, trialNum, repNum, playerId)  %>%
  summarise(total_num_words = sum(utt_length_words),
            mlu = mean(utt_length_words))

ggplot(d_flowers_utt_length, aes(x=repNum, y=total_num_words, color=as.factor(playerId)))+
  scale_color_brewer(palette="Dark2")+
  facet_grid(cols = vars(blockNum), rows =vars(gameId)) +
  geom_jitter(alpha=.05)+
  geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  stat_summary(fun.data = "mean_cl_boot")+
  scale_y_continuous(limits = c(0,50))+
  labs(title="Number of words", y="Total number of words", x="Round number", color="playerId")+
  theme(legend.position="bottom") + 
  theme_bw()

ggplot(d_flowers_utt_length, aes(x=repNum, y=mlu, color=as.factor(playerId)))+
  scale_color_brewer(palette="Dark2")+
  facet_grid(cols = vars(blockNum), rows =vars(gameId)) +
  geom_jitter(alpha=.05)+
  geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  stat_summary(fun.data = "mean_cl_boot")+
  scale_y_continuous(limits = c(0,15))+
  labs(title="MLU", y="MLU", x="Round number", color="playerId")+
  theme(legend.position="bottom") + 
  theme_bw()

### 2. Number of turns
```{r number_of_turns}

d_flowers_n_turns <- d_flowers %>%
  group_by(gameId, blockNum, trialNum, repNum, playerId)  %>%
  summarise(n=n())

ggplot(d_flowers_n_turns, aes(x=trialNum, y=n, color=as.factor(playerId)))+
  facet_grid(rows =vars(gameId)) +
  scale_color_brewer(palette="Dark2")+
  geom_jitter(alpha=.05)+
  geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  stat_summary(fun.data = "mean_cl_boot")+
  labs(title="Number of turns", y="Number of turns", x="Round number", color="playerId")+
  theme(legend.position="bottom") + 
  theme_bw()

#second plot
### 2b. Number of turns

```{r number_of_turns2}

@@

ggplot(d_flowers_n_utt_speaker, 
       aes(x=trialNum, y=n_utt_speaker, label=playerId)) + 
  geom_smooth(method = "lm", formula = y~x) + 
  geom_point(alpha=.1) +
  facet_grid(~playerId) +
  xlab("Round number") + 
  ylab("Number of turns") + 
  theme_bw()
```

@@

ttr <- function(text_){
  text_ <- tolower(text_)
  total_words = sapply(strsplit(text_, " "), length)
  no_duplicates = vapply(lapply(strsplit(text_, " "), unique), paste, character(1L), collapse = " ")
  total_unique = str_count(no_duplicates, "\\W+") + 1
  ttr_ = total_unique/total_words
  return(ttr_)
}

d_flowers_text <- d_flowers %>%
    group_by(gameId, blockNum, trialNum, repNum, playerId) %>%
    mutate(text_block = paste0(text, collapse = " ")) %>%
    select(-c(text)) %>%
    distinct()

d_flowers_ttr <- d_flowers_text %>%
  mutate(ttr_ = ttr(text_block))

#t<-str_split(text_, " ", 1:6)
#y<- paste(unlist(lapply(t,head,n=5)), collapse=" ")

ggplot(d_flowers_ttr, 
       aes(x=trialNum, y=ttr_, label=playerId)) + 
  geom_smooth(method = "lm", formula = y~x) + 
  geom_point(alpha=.1) +
  facet_grid(rows =vars(gameId)) +
  xlab("Round number") + 
  ylab("Type_token ratio") + 
  theme_bw()

@@

ggplot(d_flowers_n_utt_dist, 
       aes(x=trialNum, y=overall_turns, label=playerId)) + 
  geom_smooth(method = "lm", formula = y~x) + 
  geom_point(alpha=.1) +
  facet_wrap(~playerId)+
  xlab("Round number") + 
  ylab("Proportion of turns") + 
  theme_bw()
